%% William Fauriat - One-Page Resume
%% Compile with: pdflatex resume.tex

\documentclass[10pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter} % Charter font for better screen rendering
\usepackage[margin=0.45in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\setlength{\parskip}{0pt}

% Custom color
\definecolor{accentcolor}{RGB}{79,70,229}  % Indigo
\definecolor{darkgray}{RGB}{64,64,64}
\definecolor{mediumgray}{RGB}{102,102,102}

% Hyperlink styling
\hypersetup{
    colorlinks=true,
    linkcolor=accentcolor,
    urlcolor=accentcolor,
    pdftitle={William Fauriat - Resume},
    pdfauthor={William Fauriat}
}

% Section formatting
\titleformat{\section}
  {\large\bfseries\color{accentcolor}}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{2pt}

% Subsection formatting (for job titles)
\titleformat{\subsection}[runin]
  {\bfseries}
  {}{0em}{}
\titlespacing*{\subsection}{0pt}{6pt}{0pt}

% Remove page numbers
\pagestyle{empty}

% Custom commands
\newcommand{\resumeitem}[1]{\item\small{#1}}
\newcommand{\experience}[4]{
  \textbf{#1} \hfill \textcolor{mediumgray}{#2}\\
  \textit{\color{mediumgray}#3}%
  #4
  \vspace{1mm}
}

% Reduce list spacing
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*, before=\vspace{-0.5mm}, after=\vspace{1mm}}

\begin{document}

% ========== HEADER ==========
\begin{center}
  {\LARGE\bfseries\color{accentcolor} WILLIAM FAURIAT}\\[1mm]
  {\normalsize Senior Data Scientist building models for production}\\[2mm]
  \href{mailto:wfauriat@gmail.com}{wfauriat@gmail.com} ~|~
  \href{https://wfauriat.github.io}{wfauriat.github.io} ~|~
  \href{https://github.com/wfauriat}{github.com/wfauriat} ~|~
  \href{https://www.linkedin.com/in/william-fauriat}{linkedin.com/in/william-fauriat}
\end{center}

\vspace{1mm}

% ========== PROFESSIONAL SUMMARY ==========
\section*{Professional Summary}
\small
10+ years in Statistics and Data Science for industrial applications and scientific computing.
Senior researcher in Uncertainty Quantification leveraging stochastic modeling and statistical
learning for decision-making. Current focus: turning research into production APIs and full-stack ML applications.

% ========== EXPERIENCE ==========
\section*{Experience}

\experience{Senior Data Scientist}{2021--present}{CEA (French Atomic Energy Commission)}{
\begin{itemize}
  \resumeitem{Fine-tuned inversion algorithms for high-power tomography}
  \resumeitem{Designed data processing APIs and visualization tools for model calibration}
  \resumeitem{Led Bayesian Optimization of experimental conditions for Inertial Confinement Fusion}
  \resumeitem{Leading training on Uncertainty Quantification (20+ persons)}
\end{itemize}
}

\experience{Post-Doctoral Researcher}{2018--2020}{CentraleSupélec (French Grande École)}{
\begin{itemize}
  \resumeitem{Research on optimal information collection for decision under uncertainty}
  \resumeitem{Published Value of Information framework for maintenance optimization}
  \resumeitem{Bayesian decision theory applied to conditional maintenance scheduling}
  \resumeitem{100+ hours courses on reliability and industrial engineering}
\end{itemize}
}

\textbf{Gap Year} — \textit{Travelling} \hfill \textcolor{mediumgray}{2017}
\vspace{1mm}

\experience{Consultant}{2016}{ALTEN for PSA (now Stellantis — automotive manufacturer)}{
\\
Product development engineer working on design and validation of suspension system architecture
}

\experience{PhD Researcher}{2013--2016}{Renault (automotive manufacturer)}{
\begin{itemize}
  \resumeitem{Stochastic modeling of road-induced fatigue loads on suspension systems}
  \resumeitem{Published road profile identification method using Kalman filtering}
\end{itemize}
}

% ========== EDUCATION ==========
\section*{Education}

\experience{PhD, Mechanical \& Industrial Engineering}{2016}{Université Clermont Auvergne}{
\textit{Dissertation:} "Stochastic modeling of road-induced fatigue loads on suspension systems"
}

\experience{Engineering degree (Master's level)}{2012}{IFMA (French Grande École)}{}

\experience{Full-Stack Engineer Certification}{2024}{Codecademy}{
150+ hours online courses, projects \& exams: React, Node.js, Express, REST APIs, SQL, Git, CI/CD
}

% ========== SKILLS ==========
\section*{Skills}

\begin{minipage}[t]{0.48\textwidth}
\textbf{Core Competencies}
\begin{itemize}
  \resumeitem{Bayesian Inference}
  \resumeitem{Uncertainty Quantification}
  \resumeitem{Machine Learning}
  \resumeitem{Statistical Decision Theory}
  \resumeitem{Full-Stack Development}
  \resumeitem{API Design}
  \resumeitem{AI-enhanced Development}
  \resumeitem{Scientific Computing}
\end{itemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\textbf{Tech Stack}
\begin{itemize}
  \resumeitem{\textbf{Languages:} Python (expert), JavaScript (proficient), SQL}
  \resumeitem{\textbf{Backend:} Flask, FastAPI, NumPy, SciPy, scikit-learn}
  \resumeitem{\textbf{Frontend:} React, HTML/CSS, PyQt5}
  \resumeitem{\textbf{Tools:} Git, Docker, Linux}
\end{itemize}
\end{minipage}

% ========== PUBLICATIONS ==========
\section*{Selected Publications}

\small
\textbf{[1]} Fauriat, W. \& Zio, E. (2020). Optimization of an aperiodic sequential inspection and condition-based maintenance policy driven by value of information. \textit{Reliability Engineering \& System Safety}, 204, 107133.

\textbf{[2]} Fauriat, W., Mattrand, C., Gayton, N., Beakou, A., \& Cembrzynski, T. (2016). Estimation of road profile variability from measured vehicle responses. \textit{Vehicle System Dynamics}, 54(5), 585-605.

\textbf{[3]} Fauriat, W. \& Gayton, N. (2014). AK-SYS: An adaptation of the AK-MCS method for system reliability. \textit{Reliability Engineering \& System Safety}, 123, 137-144.

% ========== PROJECTS ==========
\section*{Selected Projects}

\textbf{Bayesian Inference Web App:} Production-deployed full-stack application for interactive Bayesian inference. NumPy-only inference engine, Flask backend, React frontend. \textit{Tech:} Python, NumPy, Flask, React, scikit-learn | \href{https://bi-webapp.onrender.com}{bi-webapp.onrender.com}

\textbf{UQ Initiation App:} Standalone desktop tool for learning uncertainty quantification through interactive simulations. \textit{Tech:} Python, PyQt5

\end{document}
